---
title: "Towards Visualizing Data"
author: "Ana Martins"
date: "November 2022"
output: html_document
---

1. **Name the aesthetics, geoms, scales and facets of the above visualization. Also name any statistical transformations or special coordinate systems.**

Aesthetics
- x is mapped to Hits
- y is mapped to Home runs

Geoms:
- points
- countour lines

Scales:
- x is continous
- y is continuous

Facets:
- none

Statistical Transformations:
- none

Special Coordinate System:
- non (just the cartesian)

2. `**Run the code below to generate data. There will be three vectors in your environment. Put them in a data frame for entering it in a `ggplot()` call using either the `data.frame()` or the `tibble()` function. Give informative names and make sure the types are correct (use the `as.<type>()` functions). Name the result `gg_students``.**

```{r}
set.seed(45)
student_grade <- rnorm(32, 7)
student_number <- round(runif(32) * 2e6 + 5e6)
programme <- sample(c("Science", "Social Science"), 32, replace = TRUE)
```

```{r}
gg_students <-
  tibble(student_number = as.numeric(student_number), programme = as.factor(programme), student_grade = as.numeric(student_grade))
```

3. **Plot the first `homeruns_plot` again, but map the `Hits` to the y-axis and the `HmRun` to the x-axis instead.

```{r}
Hitters %>% 
  ggplot(aes(x = HmRun, y = Hits)) +
  geom_point() +
  labs(x = "Home Runs", y = "Hits") +
  theme_minimal()
```

4. **Recreate the same plot once more, but now also map the variable